Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-07 longoutput.tex
Write down all Hamiltonians
Change notation for CCU gates

We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H_f=H_f\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.

@@

First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
We also set $S_{legal}=\ker H_{clock}$. Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register. Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates.
$$H_{clock}=\frac{1}{4}((T-1)I + Z_1 - Z_T - \sum_t^{T-1}Z_tZ_{t+1})$$

@@

I probably need to explain why this works but I'll leave it for another day.

>>>>

We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H_f=H_f\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0)\Lambda^2_{f,s}(Z_0)\circ T=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ T$$
Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.

@@

First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
We also set $S_{legal}=\ker H_{clock}$. Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register. Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates. TODO check if this is obvious. If not, explain why.
$$H_{clock}=\frac{1}{4}((T-1)I + Z_1 - Z_T - \sum_t^{T-1}Z_tZ_{t+1})$$

@@

I probably need to explain why this works but TODO I'll leave it for another day.

Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli. Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
So we can write
$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$

### 2019-09-07 preliminaries.tex
start rewriting local Hamiltonian reduction
Change notation for CCU gates

\begin{definition}
	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$. $\Lambda_{f, s}(U)$ would be the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda{1, 2}(X_3)$ would be a Toffoli ((CCNOT) gate.
\end{definition}

\begin{definition}
	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$
\end{definition}

>>>>

\begin{definition}
	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$, $X=\begin{pmatrix}0&1\\1&0\end{pmatrix}$, $Z=\begin{pmatrix}1&0\\0&-1\end{pmatrix}$
\end{definition}

\begin{definition}
	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$, and $\Lambda^2_{f, s}(U)$ denote the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda^2{1, 2}(X_3)$ would be a Toffoli (CCNOT) gate.
\end{definition}
